Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-06-28 SWoPP2018 Paper/paper.tex
Added code project.

\usepackage[dvips]{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{adjustbox}

@@

\subsection{(Convolutional) Neural Networks}
Small intro to Neural Networks.

\subsection{FPGA CNN Framework}
Small intro to the framework.
\subsubsection{Design overview}
Overview design + picture.
\subsubsection{Design details}
Gruesome details of the design.
\subsubsection{Design decisions}
Decisions taken while designing. The *why* we did as we did.

\section{Methodology}
\label{sec:method}
\subsection{Experimental Platform}
Compiler, version, flags, fpga boards, host, etc.
\subsection{Network Tested + Data-set}
MNIST, Multilayer Perceptron?
number of runs, batch size, etc.

\section{Results}
\label{sec:result}

@@

\section{Conclusion}
\label{sec:conclusion}

>>>>

\usepackage[dvips]{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{siunitx}

@@

\subsection{Neural Networks}
Intro to neural networks.

\subsection{FPGA NN Framework}
Small intro to the framework.
\subsubsection{Design overview}
Overview design + picture.
\subsubsection{Design details}
All weight matrices are transposed in memory.
The main inference is done using an blocking implementation of the matrix multiplication.
So a block is fetched from the activations and the wieghts and place in the block RAM on the FPGA.
The block RAM is much faster then the global memory.
This speeds up through put by a large margin.
Block RAM is equivalent to the shared or local memory of contemporary GPUs.

\subsubsection{Design decisions}
Decisions taken while designing. The *why* we did as we did.

\section{Methodology}\label{sec:method}
\subsection{Experimental Platform}
\begin{table}[h]\label{tab:software-versions}
  \caption{Used software versions}
  \begin{tabular}{ll}
    \toprule
    \textbf{Software} & \textbf{Version} \\
    \midrule
    Python & v3.6.3 \\
    Keras & v2.2.0 \\
    TensorFlow & v1.8.0 \\
    Intel Quartus & v17.1.0 \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[h]\label{tab:test-hardware}
  \caption{Test hardware}
  \begin{tabular}{ll}
    \toprule
    \textbf{Hardware} & \textbf{Configuration} \\
    \midrule
    Intel i7-3930K & 3.20 GHz \\
    Arria 10 & Nallatech N510T \\
    TensorFlow & v1.8.0 \\
    Intel Quartus & v17.1.0 \\
    \bottomrule
  \end{tabular}
\end{table}
Compiler, version, flags, fpga boards, host, etc.
\subsection{Network Tested + Data-set}
The used example network is a simple multilayer perceptron.
The main dataset used was MNIST with a layer depth of 1 and the first layer output size of 128.
The data set was trained using the first \num{50000} images from the MNIST dataset.
The last \num{10000} images are used as the test dataset.
Training was done using a batch size of 128.

\section{Results}\label{sec:result}

@@

\section{Conclusion}\label{sec:conclusion}
